Moral Foundations of U.S. Political News Organizations

### 2019-01-03 pilot_manuscript.Rmd
Exp1 Results expansion; outline Exp1 discussion

@@

apa_table(tableprint,
          note = "something useful here",
          caption = "stuff at the top", 
          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 7))
          )
```
# Discussion

>>>>

The multilevel model did not indicate the presence of any significant or practical effect of political lean for any of the five moral foundations. The strongest effect size was observed for the *authority/respect* foundation, but the effect was in the opposite direction from what was originally hypothesized - liberal sources tended to use more *authority/respect* words than did conservative sources. Descriptive and test statistics, *p*-values and effect sizes (Cohen's *d*) can be found in Table 1.

@@

apa_table(tableprint,
          note = "something useful here",
          caption = "stuff at the top", 
          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 7))
          )
```
# Discussion 
What we found - nothing really, even some disconfirming evidence, but it wasn't sig and eff size was small.

Why it might not have worked (focus too broad??)

Well, this was exploratory anyway, so lets firm up the method and try another way. How about a polarizing and morally-focused singular issue?? Which leads us to Experiment 2, in which we hope to confirm the method!!
